A Comparison of Graph Processing Systems

### 2020-09-03 documentation/paper/sections/overview/giraph.tex
added pregel info, moved Mapreduce from giraph to preliminiaries, giraph is now ugly again

TODO // MapReduce hier oder wo anders erklären?
MapReduce is a in three phases
\begin{enumerate}
	\item Map phase: The input data is distributed between a set of map processes, the map functionality is specified by the user. Ideally all map processes run in parallel so the map processes need to be independent. Results from this phase are written into (multiple) intermediate storage points.
	\item Shuffle phase: The results are grouped according to a key provided by the map algorithm. Each set of results is then handed to one system for the next phase.
	\item Reduce phase: Every set of intermediate results is input to exactly one reduce process. The reduce functionality is again specified by the user and ideally runs in parallel.
\end{enumerate}
Giraph uses the Map functionality of Hadoop to run the algorithms, Reduce is only used as an identity function.

Giraph's computation model is closely related to the BSP model discussed in \autoref{sec:bsp}. This means that Giraph is based on computation units that communicate using messages and are synchonized with barriers.

>>>>

Giraph is an example for an open-source system similar to Pregel.
Thus, Giraph's computation model is closely related to the BSP model discussed in \autoref{sec:bsp}. 
//TODO: Hier wiederholt sich jetzt einiges.. ärgerlich.

// Mapreduce: Giraph uses the Map functionality of Hadoop to run the algorithms, Reduce is only used as an identity function.

This means that Giraph is based on computation units that communicate using messages and are synchonized with barriers.

### 2020-09-03 documentation/paper/sections/preliminiaries.tex
Ligra writeup
added pregel info, moved Mapreduce from giraph to preliminiaries, giraph is now ugly again

\subsection{Pregel Model}

% Google, to overcome, these challenges came up with Pregel.
% Provides scalability
% Fault-tolerance
% Flexibility to express arbitrary algorithms
% The high level organization of Pregel programs
% is inspired by Valiant’s Bulk Synchronous
%  Parallel model 
\subsection{Congest Model}

>>>>

One of the most famous state-of-the-art graph processing systems is Pregel \cite{pregel}. It is based on the BSP computation model.
Pregel and many open-source versions similar to it were built to process large graphs reliably (offering fault tolerance) on large MapReduce infrastructures.

\subsection{MapReduce}
The MapReduce model is a computation infrastructure developed by Google to reliably handle large data sets on distributed clusters \cite{mapreduce}.

A user specifies just the two functions Map and Reduce.
The system hides the details of parallelization, fault-tolerance, data distribution and load balancing away from the application logic.
All of these features are automatically provided.

Execution is performed in three phases:
\begin{enumerate}
	\item Map phase: The input data is distributed between a set of Map processes, the Map functionality is specified by the user. Ideally all Map processes run in parallel so the map processes need to be independent. Results from this phase are written into (multiple) intermediate storage points.
	\item Shuffle phase: The results are grouped according to a key provided by the Map algorithm. Each set of results is then handed to one system for the next phase.
	\item Reduce phase: Every set of intermediate results is input to exactly one reduce process. The Reduce functionality is again specified by the user and ideally runs in parallel.
\end{enumerate}

We show Giraph \cite{Giraph} as an example of a system using this framework.

\subsection{Congest Model}
